Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-18 paper/Paper.tex
White paper buy/create sale/creation changes

\begin{abstract}
This paper describes the first implementation of Decentralized Autonomous Organization (DAO) code to automate organizational governance and decision-making. The code can be used by individuals working together collaboratively outside of a traditional corporate form. It can also be used by a registered corporate entity to automate formal governance rules contained in corporate bylaws or imposed by law. First the DAO Concept is described, then minority rights is discussed, and a solution to a ``robbing the minority'' attack vector isproposed. Finally, a practical implementation of a first generation DAO entity is provided using smart contracts written in Solidity on the Ethereum blockchain.
\end{abstract}

@@

\section{Token Price} \label{TokenPrice}
DAO Token Creation schedule increases over time. This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO. 
The DAO described in this paper has the following Creation schedule:
\begin{equation}
 P(t) = \begin{cases}
1 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
1 + 0.05 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
1.5 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in its base unit) each buyer Creates is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel the DAO, denoted in wei.
This results in a constant Creation rate in the beginning, until $2$ weeks before the end of the DAO Creation Phase. At this time the Creation rate increases daily by $0.05 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant Creation rate of $1.5 \: \Xi_c$ per base unit of DAO token.

Creation rate increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens at the initial Creation rate, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having fueled a DAO at a higher Creation rate (\cite{GriffDiscussion}).
In order to avoid that possibility, all ether that is used to fuel the DAO above the initial Creation rate, will be sent to an extra account. Denoted as \verb|extraBalance| in \ref{app:TokenSale}. This ether can be sent back to the DAO through a proposal after the DAO has spent at least this amount of ether.
This rule is implemented in the internal function \verb|isRecipientAllowed| in section \ref{DAO}.

@@

The main contract is called 'DAO'. It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenSale'. ‘Token’ defines the inner workings of the DAO Token and ‘TokenSale’ defines how the DAO token is purchased for ether. In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from a contractor to the DAO could look like.
\end{multicols}

@@

The map \verb|balances| stores the number of DAO tokens which are controlled by an address. All contracts which derive from \verb|TokenInterface| can directly modify this map, but only $4$ functions do so: \verb|buyTokenProxy|, \verb|transfer| , \verb|transferFrom| and \verb|splitDAO|.

@@

\subsection{TokenSale}
\begin{verbatim}
contract TokenSaleInterface {
    uint public closingTime;   
    uint public minValue;  
    bool public isFueled;
    address public privateSale;
    ManagedAccount extraBalance;
    mapping (address => uint256) weiGiven;

    function TokenSale(uint _minValue, uint _closingTime);
    function buyTokenProxy(address _tokenHolder) returns (bool success);
    function refund();
    function divisor() returns (uint divisor);

    event FundingToDate(uint value);
    event SoldToken(address indexed to, uint amount);
    event Refund(address indexed to, uint value);
}
\end{verbatim}
\begin{multicols}{2}
Above is the interface of the \verb|TokenSale| contract (\ref{app:TokenSale}).

The integer \verb|closingTime| is the (unix) time at which the token sale ends.

@@

The address \verb|privateSale| is used for DAO splits - if it is set to 0, then it is a public sale, otherwise, only the address stored in \verb|privateSale| is allowed to purchase tokens.

The managed account (\ref{app:ManagedAccount}) \verb|extraBalance| is used to hold the excess ether which is received after the token price is increased during the sale. Anything that has been paid above the initial price goes to this account.

The map \verb|weiGiven| stores the amount of wei given by each contributor during the sale and is only used to refund the contributors if the Token sale does not reach its funding goal.

The constructor \verb|TokenSale| initiates the token sale with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateSale|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed. 
In order to interact with the contract the following functions can be used:

\subsubsection*{buyTokenProxy}
This function creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $20 / P(t)$ , as described in section \ref{TokenPrice}.
The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.

\subsubsection*{refund}
This function can be called by any contributor to recieve their wei back if the token sale failed to meet its funding goal.

\subsubsection*{divisor}
This function is used to calculate the price of the token during the sale in the function \verb|buyTokenProxy|.

The events \verb|FundingToDate|, \verb|SoldToken| and \verb|Refund| are used to inform lightweight clients of the status of the token sale.
\end{multicols}

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function emergenyCloseProposal(uint _proposalID) external;
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);

@@

There is a special function which is called the constructor. It has the same name as the contract ``DAO.'' This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|curator|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount|
 \item \verb|DAOrewardAccount|
 \item \verb|minValue|
 \item \verb|closingTime|
 \item \verb|privateSale|
 \item \verb|lastTimeMinQuorumMet|
 \item \verb|minQuorumDivisor|
 \item \verb|allowedRecipients|
\end{itemize}

@@

\subsubsection*{fallback function}
The fallback function is a function without a specific name. It is called when the contract receives a transaction without data (a pure value transfer). There are no direct arguments for this function.
The fallback function will call \verb|buyTokenProxy| passing the address of the sender as an argument during the token sale. This will trigger the immediate purchase of tokens. In order to protect users, this function will send the ether received after the end of the sale back to the sender for a time period of $40$ days. After which this function is repurposed to receive ether as simple deposit to the DAO using the function \verb|receiveEther|.

@@

\subsubsection*{emergenyCloseProposal}
This is used in the case `executeProposal` fails because it throws (e.g. when returuning the deposit, because the fallback function of this address throws, or when executing the proposed transaction). It can be called $5$ days after the voting deadline of the proposal passed. It will close the proposal.
\subsubsection*{splitDAO}
After a new Curator has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new Curator. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newCurator] The address of the new Curator of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively buy tokens of the newly created DAO and fund the new DAO just as the original DAO was funded.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|retrieveDAOReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed. It is important to notice that in all integer division descirbed above, there may be remainders which stay with the DAO.

@@

\subsection{TokenSale}\label{app:TokenSale}
\begin{verbatim}
contract TokenSaleInterface {

    // End of token sale, in Unix time
    uint public closingTime;
    // Minimum fueling goal of the token sale, denominated in ether
    uint public minValue;
    // True if the DAO reached its minimum fueling goal, false otherwise
    bool public isFueled;
    // For DAO splits - if privateSale is 0, then it is a public sale, otherwise
    // only the address stored in privateSale is allowed to purchase tokens
    address public privateSale;
    // hold extra ether which has been paid after the DAO token price has increased
    ManagedAccount public extraBalance;
    // tracks the amount of wei given from each contributor (used for refund)
    mapping (address => uint256) weiGiven;

    /// @dev Constructor setting the minimum fueling goal and the
    /// end of the Token Sale
    /// @param _minValue Token Sale minimum fueling goal
    /// @param _closingTime Date (in Unix time) of the end of the Token Sale
    /// @param _privateSale Zero means that the sale is public.  A non-zero
    /// address represents the only address that can buy Tokens (the address
    /// can also buy Tokens on behalf of other accounts)
    // This is the constructor: it can not be overloaded so it is commented out
    //  function TokenSale(
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateSale
    //  );

    /// @notice Buy Token with `_tokenHolder` as the initial owner of the Token
    /// @param _tokenHolder The address of the Tokens's recipient
    /// @return Whether the purchase was successful
    function buyTokenProxy(address _tokenHolder) returns (bool success);

    /// @notice Refund `msg.sender` in the case the Token Sale didn't reach its
    /// minimum fueling goal
    function refund();

    /// @return The divisor used to calculate the token price during the sale
    function divisor() returns (uint divisor);

    event FundingToDate(uint value);
    event SoldToken(address indexed to, uint amount);
    event Refund(address indexed to, uint value);
}

contract TokenSale is TokenSaleInterface, Token {
    function TokenSale(uint _minValue, uint _closingTime, address _privateSale) {
        closingTime = _closingTime;
        minValue = _minValue;
        privateSale = _privateSale;
        extraBalance = new ManagedAccount(address(this));
    }

    function buyTokenProxy(address _tokenHolder) returns (bool success) {
        if (now < closingTime && msg.value > 0
            && (privateSale == 0 || privateSale == msg.sender)) {

            uint token = (msg.value * 20) / divisor();
            extraBalance.call.value(msg.value - token)();
            balances[_tokenHolder] += token;
            totalSupply += token;
            weiGiven[_tokenHolder] += msg.value;
            SoldToken(_tokenHolder, token);
            if (totalSupply >= minValue && !isFueled) {
                isFueled = true;
                FundingToDate(totalSupply);
            }
            return true;
        }
        throw;
    }

@@

    function divisor() returns (uint divisor) {
        // The number of (base unit) tokens per wei is calculated
        // as `msg.value` * 20 / `divisor`
        // The fueling period starts with a 1:1 ratio
        if (closingTime - 2 weeks > now) {
            return 20;
        // Followed by 10 days with a daily price increase of 5%
        } else if (closingTime - 4 days > now) {
            return (20 + (now - (closingTime - 2 weeks)) / (1 days));
        // The last 4 days there is a constant price ratio of 1:1.5
        } else {
            return 30;
        }
    }
}
\end{verbatim}
\subsection{DAO}\label{app:DAO}
\begin{verbatim}
contract DAOInterface {

    // The amount of days for which people who try to participate in the sale
    // by calling the fallback function will still get their ether back
    uint constant saleGracePeriod = 40 days;
    // The minimum debate period that a generic proposal can have
    uint constant minProposalDebatePeriod = 2 weeks;
    // The minimum debate period that a split proposal can have
    uint constant minSplitDebatePeriod = 1 weeks;
    // Period of days inside which it's possible to execute a DAO split
    uint constant splitExecutionPeriod = 27 days;
    // Period of time after which the minimum Quorum is halved
    uint constant quorumHalvingPeriod = 52 weeks;
    // Period after which a proposal can be closed (used in the case `executeProposal`
    // fails because it throws)
    uint constant executeProposalPeriod = 5 days;

    // Proposals to spend the DAO's ether or to choose a new Curator
    Proposal[] public proposals;
    // The quorum needed for each proposal is partially calculated by
    // totalSupply / minQuorumDivisor
    uint minQuorumDivisor;
    // The unix time of the last time quorum was reached on a proposal
    uint lastTimeMinQuorumMet;

    // Address of the Curator
    address public curator;
    // The whitelist: List of addresses the DAO is allowed to send ether to
    mapping (address => bool) public allowedRecipients;

@@

    /// @dev Constructor setting the Curator and the address
    /// for the contract able to create another DAO as well as the parameters
    /// for the DAO Token Sale
    /// @param _curator The Curator
    /// @param _daoCreator The contract able to (re)create this DAO
    /// @param _proposalDeposit The deposit to be paid for a regular proposal
    /// @param _minValue Minimal value for a successful DAO Token Sale
    /// @param _closingTime Date (in Unix time) of the end of the DAO Token Sale
    /// @param _privateSale If zero the DAO Token Sale is open to public, a
    /// non-zero address means that the DAO Token Sale is only for the address
    // This is the constructor: it can not be overloaded so it is commented out
    //  function DAO(
        //  address _curator,
        //  DAO_Creator _daoCreator,
        //  uint _proposalDeposit,
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateSale
    //  );

    /// @notice Buy Token with `msg.sender` as the beneficiary
    /// @return Whether the purchase was successful
    function () returns (bool success);

@@

    event ProposalAdded(
        uint indexed proposalID,
        address recipient,
        uint amount,
        bool newCurator,
        string description
    );
    event Voted(uint indexed proposalID, bool position, address indexed voter);
    event ProposalTallied(uint indexed proposalID, bool result, uint quorum);
    event NewCurator(address indexed _newCurator);
    event AllowedRecipientAdded(address indexed _recipient);
}

// The DAO contract itself
contract DAO is DAOInterface, Token, TokenSale {

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateSale
    ) TokenSale(_minValue, _closingTime, _privateSale) {

@@

    function () returns (bool success) {
        if (now < closingTime + saleGracePeriod)
            return buyTokenProxy(msg.sender);
        else
            return receiveEther();
    }

@@

        // If the curator removed the recipient from the whitelist, close the proposal
        // in order to free the deposit and allow unblocking of voters
        if (!allowedRecipients[p.recipient] && p.open) {
            closeProposal(_proposalID);
            p.creator.send(p.proposalDeposit);
            return;
        }

@@

    function changeProposalDeposit(uint _proposalDeposit) noEther external {
        if (msg.sender != address(this) || _proposalDeposit > actualBalance() / 10)
            throw;
        proposalDeposit = _proposalDeposit;
    }

>>>>

\begin{abstract}
This paper describes the first implementation of Decentralized Autonomous Organization (DAO) code to automate organizational governance and decision-making. The code can be used by individuals working together collaboratively outside of a traditional corporate form. It can also be used by a registered corporate entity to automate formal governance rules contained in corporate bylaws or imposed by law. First the DAO concept is described, then minority rights is discussed, and a solution to a ``robbing the minority'' attack vector is proposed. Finally, a practical implementation of a first generation DAO entity is provided using smart contracts written in Solidity on the Ethereum blockchain.
\end{abstract}

@@

\section{Token Price} \label{TokenPrice}
DAO Token Creation rate decreases over time. This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO. 
The DAO described in this paper has the following Creation schedule:
\begin{equation}
 P(t) = \begin{cases}
1 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
1 + 0.05 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
1.5 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenCreation} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in its base unit) each person Creates is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel a DAO, denoted in wei.
This results in a constant Creation rate in the beginning, until $2$ weeks before the end of the DAO Creation Phase. At this time the amount of ether required to Create DAO tokens increases daily by $0.05 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant Creation rate of $1.5 \: \Xi_c$ per base unit of DAO token.

Creation rate decreases during the Creation Phase could lead to a situation where a single contributor, having Created DAO tokens at the initial Creation rate, could split the DAO immediately after the Creation Phase ends, thereby receiving more ether than they put in due to other contributors having fueled a DAO at a higher Creation rate (\cite{GriffDiscussion}).
In order to avoid that possibility, all ether that is used to fuel a DAO above the initial Creation rate, will be sent to an extra account. Denoted as \verb|extraBalance| in \ref{app:TokenCreation}. This ether can be sent back to the DAO through a proposal after the DAO has spent at least this amount of ether.
This rule is implemented in the internal function \verb|isRecipientAllowed| in section \ref{DAO}.

@@

The main contract is called 'DAO'. It defines the inner workings of the DAO and it derives the member variables and functions from 'Token' and 'TokenCreation'. ‘Token’ defines the inner workings of the DAO Token and ‘TokenCreation’ defines how the DAO token is purchased for ether. In addition to these three contracts, there is the 'ManagedAccount' contract, which acts as a helper contract to store the rewards which are to be distributed to the token holders and the \verb|extraBalance| (see section \ref{TokenPrice}).
The contract 'SampleOffer' (\ref{app:SampleOffer}) is an example of what a proposal from a contractor to the DAO could look like.
\end{multicols}

@@

The map \verb|balances| stores the number of DAO tokens which are controlled by an address. All contracts which derive from \verb|TokenInterface| can directly modify this map, but only $4$ functions do so: \verb|createTokenProxy|, \verb|transfer| , \verb|transferFrom| and \verb|splitDAO|.

@@

\subsection{TokenCreation}
\begin{verbatim}
contract TokenCreationInterface {
    uint public closingTime;   
    uint public minValue;  
    bool public isFueled;
    address public privateCreation;
    ManagedAccount extraBalance;
    mapping (address => uint256) weiGiven;

    function TokenCreation(uint _minValue, uint _closingTime);
    function createTokenProxy(address _tokenHolder) returns (bool success);
    function refund();
    function divisor() returns (uint divisor);

    event FuelingToDate(uint value);
    event CreatedToken(address indexed to, uint amount);
    event Refund(address indexed to, uint value);
}
\end{verbatim}
\begin{multicols}{2}
Above is the interface of the \verb|TokenCreation| contract (\ref{app:TokenCreation}).

The integer \verb|closingTime| is the (unix) time at which the Creation Phase ends.

@@

The address \verb|privateCreation| is used for DAO splits - if it is set to 0, then it is a public Creation, otherwise, only the address stored in \verb|privateCreation| is allowed to purchase tokens.

The managed account (\ref{app:ManagedAccount}) \verb|extraBalance| is used to hold the excess ether which is received after the Creation rate is decreased during the Creation Phase. Anything that has been paid above the initial price goes to this account.

The map \verb|weiGiven| stores the amount of wei given by each contributor during the Creation Phase and is only used to refund the contributors if the Creation Phase does not reach its funding goal.

The constructor \verb|TokenCreation| initiates the Creation Phase with the arguments \verb|minValue|, \verb|closingtime| and \verb|privateCreation|, which will be set in the constructor of the DAO contract (\ref{app:DAO}) which is only executed once, when the DAO is deployed. 
In order to interact with the contract the following functions can be used:

\subsubsection*{createTokenProxy}
This function creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $20 / P(t)$ , as described in section \ref{TokenPrice}.
The parameter \verb|tokenHolder| defines the receiver of the newly minted tokens.

\subsubsection*{refund}
This function can be called by any contributor to receive their wei back if the Creation Phase failed to meet its funding goal.

\subsubsection*{divisor}
This function is used to calculate the price of the token during the Creation Phase in the function \verb|createTokenProxy|.

The events \verb|FuelingToDate|, \verb|CreatedToken| and \verb|Refund| are used to inform lightweight clients of the status of the Creation Phase.
\end{multicols}

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateCreation
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function emergenyCloseProposal(uint _proposalID) external;
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);

@@

There is a special function which is called the constructor. It has the same name as the contract ``DAO.'' This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|curator|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount|
 \item \verb|DAOrewardAccount|
 \item \verb|minValue|
 \item \verb|closingTime|
 \item \verb|privateCreation|
 \item \verb|lastTimeMinQuorumMet|
 \item \verb|minQuorumDivisor|
 \item \verb|allowedRecipients|
\end{itemize}

@@

\subsubsection*{fallback function}
The fallback function is a function without a specific name. It is called when the contract receives a transaction without data (a pure value transfer). There are no direct arguments for this function.
The fallback function will call \verb|createTokenProxy| passing the address of the sender as an argument during the Creation Phase. This will trigger the immediate purchase of tokens. In order to protect users, this function will send the ether received after the end of the Creation Phase back to the sender for a time period of $40$ days. After which this function is repurposed to receive ether as simple deposit to the DAO using the function \verb|receiveEther|.

@@

\subsubsection*{emergenyCloseProposal}
This is used in the case `executeProposal` fails because it throws (e.g. when returuning the deposit, because the fallback function of this address throws, or when executing the proposed transaction). It can be called $5$ days after the voting deadline of the proposal passed. It will close the proposal.
\subsubsection*{splitDAO}
After a new Curator has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new Curator. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newCurator] The address of the new Curator of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively create tokens in the newly created DAO and fuel the new DAO just as the original DAO was fueled.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|retrieveDAOReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed. It is important to notice that in all integer division descirbed above, there may be remainders which stay with the DAO.

@@

\subsection{TokenCreation}\label{app:TokenCreation}
\begin{verbatim}
contract TokenCreationInterface {

    // End of token creation, in Unix time
    uint public closingTime;
    // Minimum fueling goal of the token creation, denominated in ether
    uint public minValue;
    // True if the DAO reached its minimum fueling goal, false otherwise
    bool public isFueled;
    // For DAO splits - if privateCreation is 0, then it is a public token
    // creation, otherwise only the address stored in privateCreation is
    // allowed to create tokens
    address public privateCreation;
    // hold extra ether which has been sent after the DAO token
    // creation rate has increased
    ManagedAccount public extraBalance;
    // tracks the amount of wei given from each contributor (used for refund)
    mapping (address => uint256) weiGiven;

    /// @dev Constructor setting the minimum fueling goal and the
    /// end of the Token Creation
    /// @param _minValue Token Creation minimum fueling goal
    /// @param _closingTime Date (in Unix time) of the end of the Token Creation
    /// @param _privateCreation Zero means that the creation is public.  A
    /// non-zero address represents the only address that can create Tokens
    /// (the address can also create Tokens on behalf of other accounts)
    // This is the constructor: it can not be overloaded so it is commented out
    //  function TokenCreation(
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateCreation
    //  );

    /// @notice Create Token with `_tokenHolder` as the initial owner of the Token
    /// @param _tokenHolder The address of the Tokens's recipient
    /// @return Whether the purchase was successful
    function createTokenProxy(address _tokenHolder) returns (bool success);

    /// @notice Refund `msg.sender` in the case the Token Creation did
    /// not reach its minimum fueling goal
    function refund();

    /// @return The divisor used to calculate the token creation rate during
    /// the creation phase
    function divisor() returns (uint divisor);

    event FuelingToDate(uint value);
    event CreatedToken(address indexed to, uint amount);
    event Refund(address indexed to, uint value);
}

contract TokenCreation is TokenCreationInterface, Token {
    function TokenCreation(uint _minValue, uint _closingTime, address _privateCreation) {
        closingTime = _closingTime;
        minValue = _minValue;
        privateCreation = _privateCreation;
        extraBalance = new ManagedAccount(address(this));
    }

    function createTokenProxy(address _tokenHolder) returns (bool success) {
        if (now < closingTime && msg.value > 0
            && (privateCreation == 0 || privateCreation == msg.sender)) {

            uint token = (msg.value * 20) / divisor();
            extraBalance.call.value(msg.value - token)();
            balances[_tokenHolder] += token;
            totalSupply += token;
            weiGiven[_tokenHolder] += msg.value;
            CreatedToken(_tokenHolder, token);
            if (totalSupply >= minValue && !isFueled) {
                isFueled = true;
                FuelingToDate(totalSupply);
            }
            return true;
        }
        throw;
    }

@@

    function divisor() returns (uint divisor) {
        // The number of (base unit) tokens per wei is calculated
        // as `msg.value` * 20 / `divisor`
        // The fueling period starts with a 1:1 ratio
        if (closingTime - 2 weeks > now) {
            return 20;
        // Followed by 10 days with a daily creation rate increase of 5%
        } else if (closingTime - 4 days > now) {
            return (20 + (now - (closingTime - 2 weeks)) / (1 days));
        // The last 4 days there is a constant creation rate ratio of 1:1.5
        } else {
            return 30;
        }
    }
}
\end{verbatim}
\subsection{DAO}\label{app:DAO}
\begin{verbatim}
contract DAOInterface {

    // The amount of days for which people who try to participate in the
    // creation by calling the fallback function will still get their ether back
    uint constant creationGracePeriod = 40 days;
    // The minimum debate period that a generic proposal can have
    uint constant minProposalDebatePeriod = 2 weeks;
    // The minimum debate period that a split proposal can have
    uint constant minSplitDebatePeriod = 1 weeks;
    // Period of days inside which it's possible to execute a DAO split
    uint constant splitExecutionPeriod = 27 days;
    // Period of time after which the minimum Quorum is halved
    uint constant quorumHalvingPeriod = 52 weeks;
    // Period after which a proposal can be closed
    // (used in the case `executeProposal` fails because it throws)
    uint constant executeProposalPeriod = 5 days;
    // Denotes the maximum proposal deposit that can be given. It is given as
    // a fraction of total Ether spent plus balance of the DAO
    uint constant maxDepositDivisor = 100;

    // Proposals to spend the DAO's ether or to choose a new Curator
    Proposal[] public proposals;
    // The quorum needed for each proposal is partially calculated by
    // totalSupply / minQuorumDivisor
    uint public minQuorumDivisor;
    // The unix time of the last time quorum was reached on a proposal
    uint  public lastTimeMinQuorumMet;

    // Address of the curator
    address public curator;
    // The whitelist: List of addresses the DAO is allowed to send ether to
    mapping (address => bool) public allowedRecipients;

@@

    /// @dev Constructor setting the Curator and the address
    /// for the contract able to create another DAO as well as the parameters
    /// for the DAO Token Creation
    /// @param _curator The Curator
    /// @param _daoCreator The contract able to (re)create this DAO
    /// @param _proposalDeposit The deposit to be paid for a regular proposal
    /// @param _minValue Minimal value for a successful DAO Token Creation
    /// @param _closingTime Date (in Unix time) of the end of the DAO Token Creation
    /// @param _privateCreation If zero the DAO Token Creation is open to public, a
    /// non-zero address means that the DAO Token Creation is only for the address
    // This is the constructor: it can not be overloaded so it is commented out
    //  function DAO(
        //  address _curator,
        //  DAO_Creator _daoCreator,
        //  uint _proposalDeposit,
        //  uint _minValue,
        //  uint _closingTime,
        //  address _privateCreation
    //  );

    /// @notice Create Token with `msg.sender` as the beneficiary
    /// @return Whether the purchase was successful
    function () returns (bool success);

@@

    event ProposalAdded(
        uint indexed proposalID,
        address recipient,
        uint amount,
        bool newCurator,
        string description
    );
    event Voted(uint indexed proposalID, bool position, address indexed voter);
    event ProposalTallied(uint indexed proposalID, bool result, uint quorum);
    event NewCurator(address indexed _newCurator);
    event AllowedRecipientChanged(address indexed _recipient, bool _allowed);
}

// The DAO contract itself
contract DAO is DAOInterface, Token, TokenCreation {

@@

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minValue,
        uint _closingTime,
        address _privateCreation
    ) TokenCreation(_minValue, _closingTime, _privateCreation) {

@@

    function () returns (bool success) {
        if (now < closingTime + creationGracePeriod)
            return createTokenProxy(msg.sender);
        else
            return receiveEther();
    }

@@

        // If the curator removed the recipient from the whitelist, close the proposal
        // in order to free the deposit and allow unblocking of voters
        if (!isRecipientAllowed(p.recipient) && p.open) {
            closeProposal(_proposalID);
            p.creator.send(p.proposalDeposit);
            return;
        }

@@

    function changeProposalDeposit(uint _proposalDeposit) noEther external {
        if (msg.sender != address(this) || _proposalDeposit > (actualBalance() + rewardToken[address(this)])
            / maxDepositDivisor) {

            throw;
        }
        proposalDeposit = _proposalDeposit;
    }
